**The Place of Interoception and Theory of Mind in Deception**

### 2021-11-22 1_Measures.Rmd
update

@@

@@

```{r warning=FALSE}

df |> 
  group_by(Participant, Answer) |> 
  summarise(Confidence = paste(insight::format_value(mean(Confidence, na.rm = TRUE)),
                               " +- ",
                               insight::format_value(sd(Confidence, na.rm = TRUE))),
            RT = paste(insight::format_value(mean(RT, na.rm = TRUE)),
                       " +- ",
                       insight::format_value(sd(RT, na.rm = TRUE)))) |> 
  arrange(Participant) |> 
  knitr::kable()
```

@@

```{r warning=FALSE}
df <- df |> 
  dplyr::filter(Participant != "S9",  # Extreme answers
                !Participant %in% c("S3", "S15", "S19", "S23"))  # No data
```

@@

```{r warning=FALSE}
p1 <- df |> 
  dplyr::filter(!Participant %in% c("S29")) |>
  ggplot(aes(x = Confidence, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  see::theme_modern() +
  scale_x_continuous(labels = scales::percent, expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p2 <- df |> 
  dplyr::filter(!Participant %in% c("S29")) |> 
  ggplot(aes(x = RT, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p1 / p2
```

>>>>

### Heartbeat Tracking Task (HTT)

```{r message=FALSE}
htt_data <- read.csv("scripts/claudia/HCT_Tracking.csv") |> 
  mutate(Participant = paste0("S", as.character(ID)),
         Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) |> 
  rename(Distance = Time_to_Rpeak)

htt_data |>
  ggplot(aes(x = Distance, fill = Condition)) +
  geom_histogram(binwidth = 0.05, alpha = 0.5, position="identity") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ID) +
  see::theme_modern()

# model <- rstanarm::stan_lmer(Distance ~ Condition + (1 + Condition | ID), data = hct_data, refresh=0, chains = 2)
# model <- glmmTMB::glmmTMB(Distance ~ Condition + (1 | ID), data = hct_data)

htt_scores <- htt_data |> 
  group_by(Participant, Condition) |> 
  summarise(HTT_Mean = mean(Distance),
            HTT_n = n()) |> 
  ungroup() |> 
  complete(Participant, Condition, fill = list(HTT_Mean = NA, HTT_n = 0)) |> 
  tidyr::pivot_wider(names_from = "Condition", values_from = c("HTT_Mean", "HTT_n"))

df <- merge(df, htt_scores, by = "Participant")
```

@@

#### Physiological Processing

```{r warning=FALSE}
df_physio <- read.csv("data/data_physio_DeceptionTask.csv") |> 
  tidyr::pivot_longer(starts_with("X"), names_to = "Time", values_to = "HeartRate") |> 
  mutate(Time = as.numeric(str_remove(Time, "X"))-500,
         group = paste0(ID, condition, instruction),
         condition = fct_recode(condition, "Interrogation" = "Social"),
         instruction = fct_relevel(instruction, "TRUTH")) |> 
  group_by(condition, instruction, Time) |> 
  summarise(HeartRate = mean(HeartRate)) |> 
  ungroup()

df_physio |> 
  ggplot(aes(x = Time, y = HeartRate)) +
  geom_rect(aes(xmin=1500, xmax=2500, ymin=-65, ymax=90), alpha=0.1, fill = "green") +
  geom_line(aes(color = condition, linetype = instruction), size=1) +
  geom_vline(aes(xintercept=0), linetype = "dotted") +
  labs(y = "Average Heart Rate (bpm)", x = "Time (ms)") +
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  theme(legend.position = "top", legend.title=element_blank())
```

@@

```{r warning=FALSE}
df |> 
  group_by(Participant, Answer) |> 
  summarise(Confidence = paste(insight::format_value(mean(Confidence, na.rm = TRUE)),
                               " +- ",
                               insight::format_value(sd(Confidence, na.rm = TRUE))),
            RT = paste(insight::format_value(mean(RT, na.rm = TRUE)),
                       " +- ",
                       insight::format_value(sd(RT, na.rm = TRUE)))) |> 
  arrange(Participant) |> 
  knitr::kable()
```

@@

```{r warning=FALSE}
df <- df |> 
  # Remove participants
  dplyr::filter(Participant != "S9",  # Extreme answers
                !Participant %in% c("S3", "S15", "S19", "S23")) |>  # No data
  group_by(Participant) |> 
  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore_robust", threshold = qnorm(0.999))),
         Outliers_Physio = as.logical(performance::check_outliers(ECG_Rate_Mean_2.5s, method = "zscore_robust", threshold = qnorm(0.999))))
  ungroup()
```

```{r warning=FALSE}
df |> 
  group_by(Participant) |> 
  summarise(Physio = sum(Outliers_RT) / n(),
            RT = sum(Outliers_Physio) / n()) |> 
  tidyr::pivot_longer(-Participant, names_to = "Outlier_Type") |> 
  ggplot(aes(x=Participant, y = value, fill = Outlier_Type)) +
  geom_bar(stat = "identity") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(y = "Percentage of trials") +
  ggtitle("Number of Trial Dropped Per Participant")

df$RT[df$Outliers_RT] <- NA
df$ECG_Rate_Mean_2.5s[df$Outliers_Physio] <- NA
```

@@

```{r warning=FALSE, fig.height=figheight*2}
p1 <- df |> 
  ggplot(aes(x = Confidence, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(labels = scales::percent, expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p2 <- df |> 
  ggplot(aes(x = RT, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p3 <- df |> 
  ggplot(aes(x = ECG_Rate_Mean_2_3s, fill = Participant)) +
  geom_density(alpha = 0.1) +
  see::scale_fill_material_d(palette = "rainbow", guide = "none") +
  scale_x_continuous(expand=expansion(c(0, .05))) +
  scale_y_continuous(expand=expansion(c(0, .05))) +
  facet_wrap(~Answer)
p1 / p2 / p3
```

### 2021-11-22 2_ManipulationChecks.Rmd
update

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("YONI_"), 
         starts_with("BES_"),
         starts_with("HCT_"),
         starts_with("MAIA_"),
         starts_with("LIE_")) |> 
  group_by(Participant) |> 
  summarise_all(mean)
```

@@

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("MAIA_")),
                 select(dfsub, starts_with("HCT_")), 
                 p_adjust = "none")

@@

@@

@@

>>>>

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("YONI_"), 
         starts_with("BES_"),
         starts_with("HCT_"),
         starts_with("HTT_"),
         starts_with("MAIA_"),
         starts_with("LIE_")) |> 
  group_by(Participant) |> 
  summarise_all(mean)
```

@@

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("HTT_")),
                 select(dfsub, starts_with("HCT_")), 
                 p_adjust = "none")

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("MAIA_")),
                 select(dfsub, starts_with("HCT_"), starts_with("HTT_")), 
                 p_adjust = "none")

@@

### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(ECG_Rate_MeanRaw ~ Answer * Phrasing + (1|Participant) + (1|Item), data = df)

@@

## Lies and Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(ECG_Rate_Mean ~ Confidence * Answer + (1|Participant) + (1|Item), 
                 data = df)

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("Confidence", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

@@

### Heart Rate

```{r message=FALSE, warning=FALSE}
# ECG_Rate_Mean_2.5s
names(select(df, starts_with("ECG_")))
model <- glmmTMB(ECG_Rate_Mean_1.5_2.5s ~ Answer * Condition + (1|Participant) + (1|Item), 
                 data = dplyr::filter(df, abs(ECG_Rate_Mean_1.5_2.5s) < 10))

parameters::parameters(model, effects = "fixed")

modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

### 2021-11-22 index.Rmd
update

df <- read.csv("data/data_combined.csv") %>% 
  mutate(ID = as.factor(paste0("S", ID)),
         condition = as.factor(condition),
         item = as.factor(item),
         style = as.factor(style),
         instruction = as.factor(instruction)) |> 
  #TODO: This renaming should be done at the preprocessing stage
  rename("Participant" = "ID",
         "Condition" = "condition",
         "Item" = "item",
         "Phrasing" = "style",
         "Answer" = "instruction",
         "YONI_Total" = "yoni_total",
         "YONI_Affective" = "yoni_affective",
         "YONI_Cognitive" = "yoni_cognitive",
         "YONI_Physical" = "yoni_physical",
         "BES_Total" = "BES_total",
         "BES_Cognitive" = "BES_cognitive",
         "BES_Affective" = "BES_affective",
         "HCT_Confidence" = "HCT_confidence",
         "HCT_Accuracy" = "HCT_accuracy",
         "HCT_Awareness" = "HCT_awareness",
         "MAIA_Total" = "MAIA_total",
         "MAIA_AttentionRegulation" = "MAIA_attention_regulation",
         "MAIA_BodyListening" = "MAIA_body_listening",
         "MAIA_EmotionalAwareness" = "MAIA_emotional_awareness",
         "MAIA_NotDistracting" = "MAIA_not_distracting",
         "MAIA_NotWorrying" = "MAIA_not_worrying",
         "MAIA_Noticing" = "MAIA_noticing",
         "MAIA_SelfRegulation" = "MAIA_self_regulation",
         "MAIA_Trusting" = "MAIA_trusting",
         "LIE_Ability" = "lie_ability",
         "LIE_Frequency" = "lie_frequency",
         "LIE_Negativity" = "lie_negativity",
         "LIE_Contextuality" = "lie_contextuality",
         "Confidence" = "DT_confidence",
         "RT" = "DT_RT") |> 
  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH")) |> 
  select(-HCT_guess, -HCT_noguess, -HCT_onebreath)

>>>>

df <- read.csv("data/data_combined_wPhysio.csv") %>% 
  mutate(ID = as.factor(paste0("S", ID)),
         condition = as.factor(condition),
         item = as.factor(item),
         style = as.factor(style),
         instruction = as.factor(instruction)) |> 
  #TODO: This renaming should be done at the preprocessing stage
  rename("Participant" = "ID",
         "Condition" = "condition",
         "Item" = "item",
         "Phrasing" = "style",
         "Answer" = "instruction",
         "YONI_Total" = "yoni_total",
         "YONI_Affective" = "yoni_affective",
         "YONI_Cognitive" = "yoni_cognitive",
         "YONI_Physical" = "yoni_physical",
         "BES_Total" = "BES_total",
         "BES_Cognitive" = "BES_cognitive",
         "BES_Affective" = "BES_affective",
         "HCT_Confidence" = "HCT_confidence",
         "HCT_Accuracy" = "HCT_accuracy",
         "HCT_Awareness" = "HCT_awareness",
         "MAIA_Total" = "MAIA_total",
         "MAIA_AttentionRegulation" = "MAIA_attention_regulation",
         "MAIA_BodyListening" = "MAIA_body_listening",
         "MAIA_EmotionalAwareness" = "MAIA_emotional_awareness",
         "MAIA_NotDistracting" = "MAIA_not_distracting",
         "MAIA_NotWorrying" = "MAIA_not_worrying",
         "MAIA_Noticing" = "MAIA_noticing",
         "MAIA_SelfRegulation" = "MAIA_self_regulation",
         "MAIA_Trusting" = "MAIA_trusting",
         "LIE_Ability" = "lie_ability",
         "LIE_Frequency" = "lie_frequency",
         "LIE_Negativity" = "lie_negativity",
         "LIE_Contextuality" = "lie_contextuality",
         "Confidence" = "DT_confidence",
         "RT" = "DT_RT") |> 
  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH")) |> 
  select(-HCT_guess, -HCT_noguess, -HCT_onebreath)
